Grupo Bimbo Inventory Demand \\Data Science Report

### 2024-07-13 src/data-science-project/data_science_project/docs/paper/paper.tex
Introduction

>>>>

Data science has become a pivotal field in extracting actionable insights from vast amounts of data. In this study, we focus on a comprehensive approach to data analysis and model development, using a dataset sourced from Kaggle, supplemented by additional variables obtained through web scraping. This project aims to build predictive models to extract meaningful patterns and provide reliable predictions based on the integrated dataset.

The data was augmented with biweekly inflation rates and consumer confidence indices from an API, spanning the period from March 31st to June 1st, 2016. This augmentation was intended to enhance the dataset's robustness and provide additional context to the predictive models.

We embarked on this project with the following objectives:

Gather and preprocess the data to ensure quality and consistency.
Perform exploratory data analysis to uncover underlying patterns and relationships.
Engineer features that enhance the predictive power of the models.
Select and train multiple machine learning models to identify the most effective one.
Evaluate the models' performance and derive insights from the results.

\section{RELATED WORKS}

### 2024-07-13 src/data-science-project/data_science_project/docs/report/report.tex
Introduction

\section{Gathering Data and Exploration}
Laureado: Isamu Akasaki (Japón), Hiroshi Amano (Japón), Shuji Nakamura (Japón, Estados Unidos de América).\\
País: Japón y Estados Unidos de América
\subsection{Kaggle and Web Scrapping}
Nació el 11 de septiembre de 1960 en Hamamatsu, (Japón). Doctorado en ingeniería en 1989 por la Universidad de Nagoya, donde es catedrático. Graduado en 1983 del Departamento de Electrónica de la Facultad de Ingeniería por la Universidad de Nagoya. En 1982, se unió al grupo de Isamu Akasaki. Investigador asociado de la Universidad de Nagoya de 1988 a 1992, asistente, asociado y catedrático de la Universidad Meijo entre 1992 y 2010 y catedrático de la Universidad de Nagoya. Galardonado con el Premio Nobel 2014 de Física, junto con Isamu Akasaki y Shuji Nakamura por su invención de las luces azules LED.
\subsection{Data Exploration}
Nació el 30 de enero 1929 en Chiran, Japón. En 1952, se graduó de la Facultad de Ciencias por la Universidad de Kioto y comenzó a trabajar en la Kobe Kogyo Corporation, que forma parte de Fujitsu. En 1959, ingresó a la Universidad de Nagoya como investigador asociado en la Facultad de Ingeniería y como profesor asistente a partir de 1964 tras doctorarse. Fue reconocido por inventar el nitruro de galio brillante (GaN) azul unión p-n LED en 1989 y, posteriormente, el alto brillo azul GaN LED. Comenzó a trabajar en GaN-based blue LEDs en la década de 1960 en el Matsushita Research Institute de Tokio, Inc. (MRIT). Nombrado en 1981 catedrático de la Facultad de Ingeniería de la Universidad de Nagoya, puesto en el que se retiró en 1992.

>>>>

\section{Gathering Data and Exploration}
\subsection{Kaggle and Web Scrapping}
The dataset for this competition was primarily sourced from Kaggle. Additionally, we utilized web scraping techniques to augment our data with external variables. Specifically, we collected biweekly inflation rates and consumer confidence indices from an API. These additional variables were gathered for the period from March 31st to June 1st, 2016.
\subsection{Data Exploration}
To understand the structure and characteristics of our dataset, we employed various graphical representations and utilized the YData Profile Report. This step helped us identify the distribution of our data, detect any anomalies, and gain insights into potential relationships between variables.
